Accuracy and precision of zero-heat-flux temperature monitoring

### 2019-12-03 manuscript/manuscript.Rmd
hyperlink fixed

A systematic review was conducted in accordance with a predetermined protocol. The protocol was submitted to PROSPERO for registration but due to delays in processing we had started data extraction by the time it was reviewed. Therefore, the protocol did not meet the requirements for registration. A copy of the submitted protocol can be accessed [here](https://github.com/awconway/zhf-review). The primary comparison for this review was temperature measured from a zero-heat-flux thermometer versus temperature measured from a core site, which we defined as temperature measured at either an arterial, esophageal, bladder or rectal site. Secondary comparisons were made between zero-heat-flux thermometers and temperatures taken at peripheral sites.

@@

Published studies were found by searching Medline and EMBASE to July 2019. The Cochrane-recommended search strategy combining terms for the ‘target condition’ and ‘index test’ was used.[@mann2012should] This search strategy is an efficient approach for systematic reviews of diagnostic test accuracy studies.[@preston2015improving] We also conducted forward citation searching, by using Google Scholar to search the citations of the first article published on the accuracy of zero-heat-flux thermometers. The search strategies used for each data base can be located [here](https://aconway.dev/zhf app). Selection of studies was undertaken independently by two reviewers using [Covidence](https://www.covidence.org).

@@

```{r table-1, layout="l-page-outset"}
ma <- list(primary, low_risk, ICU, OT,  NPA,SL, conflict)
names(ma) <- c("Primary", "Low risk studies", "Intensive Care Unit", 
               "Surgery", "Nasopharyngeal", "Sublingual",
               "Studies not funded by industry")
df <- bind_rows(ma, .id="Comparison")
df %>% 
  rename(" " = Comparison, "Mean bias" = bias_mean, "Variance" = sd2_est, "Tau-squared" = tau_est, "Lower bound for 95% limit of agreement" = LOA_L, "Upper bound for 95% limits of agreement" = LOA_U, "Outer confidence interval for lower 95% limits of agreement" = CI_L_rve, "Outer confidence interval for upper 95% limits of agreement" = CI_U_rve) %>% 
    gt() %>% 
  tab_header(
    title = "Table 1. Results of meta-analyses"  )  %>% 
  tab_spanner(
    label = "Population limits of agreement",
    columns = vars(
      `Outer confidence interval for lower 95% limits of agreement`, `Outer confidence interval for upper 95% limits of agreement`)
  )
```

>>>>

A systematic review was conducted in accordance with a predetermined protocol. The primary comparison for this review was temperature measured from a zero-heat-flux thermometer versus temperature measured from a core site, which we defined as temperature measured at either an arterial, esophageal, bladder or rectal site. Secondary comparisons were made between zero-heat-flux thermometers and temperatures taken at peripheral sites.

@@

Published studies were found by searching Medline and EMBASE to July 2019. The Cochrane-recommended search strategy combining terms for the ‘target condition’ and ‘index test’ was used.[@mann2012should] This search strategy is an efficient approach for systematic reviews of diagnostic test accuracy studies.[@preston2015improving] We also conducted forward citation searching, by using Google Scholar to search the citations of the first article published on the accuracy of zero-heat-flux thermometers. The search strategies used for each data base can be located [here](https://aconway.dev/zhf). Selection of studies was undertaken independently by two reviewers using [Covidence](https://www.covidence.org).

@@

```{r table-1, layout="l-page-outset", echo=FALSE}
library(kableExtra)
  ma <- list(primary, low_risk, ICU, OT,  NPA,SL, conflict)
names(ma) <- c("Primary", "Low risk studies", "Intensive Care Unit", 
               "Surgery", "Nasopharyngeal", "Sublingual",
               "Studies not funded by industry")
df <- bind_rows(ma, .id="Comparison")
df %>% 
  rename(" " = Comparison, "Mean bias" = bias_mean, "Variance" = sd2_est, "Tau-squared" = tau_est, "Lower bound for 95% limit of agreement" = LOA_L, "Upper bound for 95% limits of agreement" = LOA_U, "Outer confidence interval for lower 95% limits of agreement" = CI_L_rve, "Outer confidence interval for upper 95% limits of agreement" = CI_U_rve) %>% 
    gt() %>%
  tab_header(
    title = "Table 1. Results of meta-analyses"  )  %>%
  tab_spanner(
    label = "Population limits of agreement",
    columns = vars(
      `Outer confidence interval for lower 95% limits of agreement`, `Outer confidence interval for upper 95% limits of agreement`)
  )
```
